A generalized definition of multidimensional item response theory parameters

### 2024-07-24 output/paper_draft/paper_M2PLM_parameters.Rmd
Discusses other "allowed" use of agnostic version

With that purpose in mind, we have defined two versions of these parameters:
One that takes into account the whole covariance structure,
and another one that only considers the correlations among latent dimensions.
The covariance-based parameter has the drawback of not fulfilling
the first of @reckase_discriminating_1991's properties, namely,
the scale invariance property.
However, we have provided a rationale for the violation of this property,
arguing that it is also paralleled in unidimensional IRT.
Given its equivalence to the inner product definition in a space with
an identity covariance matrix,
it also refers the item parameters to an orthonormal metric,
comparable among different latent spaces.
More importantly, the covariance-based version
of the multidimensional parameters is invariant to
changes of latent-space basis.
Once again, this is important in applications where
potentially different bases are involved.
Given these considerations,
we propose to adopt the covariance-based version of
the multidimensional parameters as the most general definition,
and refer to them simply as
the $`r MDISC_SYM`$ and $`r MIL_PARAM`$ parameters.
The correlation-based version, on the other hand,
has the advantage of being scale-invariant,
which is convenient for fidelity when representing the items.
However, it is worth noting that it has been defined ad-hoc
to fulfill this specific property.
Therefore, it lacks other desirable properties of the covariance-based version,
like being invariant to a latent space scaling transformation,
or yielding a diagonal latent covariance matrix in the corresponding
orthogonal latent space basis.
Therefore, we recommend its use for graphical representation purposes only.
As for the agnostic version, we recommend it only in
the (unlikely) case of having no information about the latent space structure.

>>>>

With that purpose in mind, we have defined two new versions of these parameters:
One that takes into account the whole covariance structure,
and another one that only considers the correlations among latent dimensions.
The covariance-based parameter has the drawback of not fulfilling
the first of @reckase_discriminating_1991's properties, namely,
the scale invariance property.
However, we have provided a rationale for the violation of this property,
arguing that it is also paralleled in unidimensional IRT.
Given its equivalence to the inner product definition in a space with
an identity covariance matrix,
it also refers the item parameters to an orthonormal metric,
comparable among different latent spaces.
More importantly, the covariance-based version
of the multidimensional parameters is invariant to
changes of latent-space basis.
Once again, this is important in applications where
potentially different bases are involved.
Given these considerations,
we propose to adopt the covariance-based version of
the multidimensional parameters as the most general definition,
and refer to them simply as
the $`r MDISC_SYM`$ and $`r MIL_PARAM`$ parameters.
The correlation-based version, on the other hand,
has the advantage of being scale-invariant,
which is convenient for fidelity when representing the items.
However, it is worth noting that it has been defined ad-hoc
to fulfill this specific property.
Therefore, it lacks other desirable properties of the covariance-based version,
like being invariant to a latent space scaling transformation,
or yielding a diagonal latent covariance matrix in the corresponding
orthogonal latent space basis.
Therefore, we recommend its use for graphical representation purposes only.
As for the agnostic version, we recommend it only in
the (unlikely) case of having no information about the latent space structure,
or when such structure is considered irrelevant
(e.g., plotting the discrimination parameters after an oblique rotation).
